### 2023-12-15 latex/Plusone_configs/paper.tex
MLP 调参

% line numbers
\usepackage[right]{lineno}

@@

% array package and thick rules for tables
\usepackage{array}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study
}}} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,2\Yinyang},
Name2 Surname\textsuperscript{2\Yinyang},
Name3 Surname\textsuperscript{2,3\textcurrency},
Name4 Surname\textsuperscript{2},
Name5 Surname\textsuperscript{2\ddag},
Name6 Surname\textsuperscript{2\ddag},
Name7 Surname\textsuperscript{1,2,3*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

% Current address notes
\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address
% \textcurrency c Insert third current address

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:XGBoost}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\section*{Research Methodology}
\subsection*{VIX term structures decompositions}
The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S\&P 500 Index.
\\Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date. At time $t$,
we can view lots of VIX futures contracts with different expiration dates:
\begin{eqnarray}
    {F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
\end{eqnarray}
where $i$ denote the index of the VIX futures contracts with a ascending expiration dates $T_1 < T_2 < ... < T_d$.
\\A term-structure of constant-maturity VIX futures(CMFs), consist of 1,2,...,6 months in our case, are constructed as
a linear interpolation of two nearest expiration dates VIX futures:
\begin{eqnarray}
\label{eq:defineV}
    {V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
\end{eqnarray}
where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the left of time axis,
$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the right of time axis, and
$\omega^j_t = \frac{T_{R_j} - 30j}{T_{R_j} - T_{L_j}}$. Note that $VIX_t$ is like a zero-horizon CMF.
CMFs are commonly used for they do not suffer fluctuations caused by contract expiry.

@@

% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{machine learning models}

@@

(introduction of MLP).
In our experiment, we use leaky ReLU introduced by Mass (2013) as the activation function \(\phi\) for MLP, the mathematical expression of leaky ReLU  is shown in Eq.2. Given activation function \(\phi\), features \(X \in R^ {n\times d}\) where \(x\) presents the batch size and \(d\) presents the dimensionalities
\begin{eqnarray}
\label{eq:schemeP}
\mathrm{\phi^{(i)}} =\mathbf{max({W^{(i)}}^{T}x,0)}=
\begin{cases}
\mathbf{{W^{(i)}}^{T}x},\quad &\mathbf{{W^{(i)}}^{T}x}>0\\0, \quad else
\end{cases}
\end{eqnarray}
where \(W^{(i)}\) is the weight vector of \(i_{th}\) hidden unit while \(x\) is the input features. A naive MLP can be illustrated as figure 2.
\begin{figure}[!h]
\includegraphics[width=0.5\linewidth]{MLP.jpg}
\caption{{\bf Naive MLP:} MLP network with one hidden layer}
\label{fig2}
\end{figure}

@@

\subsubsection*{2.4 Temporal Covolutional Networks}
Temporal covolutional networks (TCN), originally introduced by Lea et al. (2016), is a type of neural network that employs convolutional layers to capture dependencies in sequential data, . Unlike traditional RNN and LSTMs, TCNs use 1D convolutions to process input sequences in parallel, making them highly parallelizable and capable of capturing long-range dependencies. Implementation details can be found in eq.5.

@@

\subsubsection* {2.5 Transformer}
We also implement attention-based network architecture called transformer proposed by Vaswani et al. (2017) for prediction. Transformer departs from the traditional recurrent or convolutional layers, relying instead on the attention mechanism, This enables the model to weigh the significance of different parts of the input data differently, allowing it to capture complex dependencies and relationships within the data. Eq.6 illustrates the implementation details.

\begin{eqnarray}
\label{eq: Transformer}
    y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
\end{eqnarray}
In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
\begin{eqnarray}
\label{eq: TransformerDecoder}
    \begin {cases} \tilde{X} = \text{Positional Encoding} + X
    \\Y = FFN(\text{self-attention}(X))
    \end {cases}
\end{eqnarray}
where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
\begin{eqnarray}
\label{eq: self-attention}
    \begin {cases} Q = W^QX
    \\K = W^KX
    \\V = W^VX
    \\Z = \test{softmax}(QK^T)V
    \end {cases}
\end{eqnarray}
where $Z$ is the output of self-attention layer.

\section*{data and experiment design}

@@

 \subsubsection*{Empirical Experiment Designs}
 The main goal of our empirical experiment aims to evaluate the statistical and economic performances among different models and different datasets.
Before training we are dealing with tabular datasets with multi-index datetime and instruments, columns represents features. we form dataset {(Xi, yi)}i=1,2,..,I into a single combined dataset(X, y) to train model instead of train I models every task named "features stacking". With this dataset organization, conclusions are more general and less biased by outliers or over fitting and model can be trained with more data, correspondingly correlation of instruments are not considered in the model.

\subsubsection*{Trading Strategy: A mean-variance approach}
To ascertain optimal portfolio weights grounded in forecasted data, we employed mean-variance optimization incorporating additional constraints. The covariance structure was derived through the estimation of a 60-day historical covariance matrix. The risk aversion parameter, denoted as gamma, was fixed at a value of 0.2.
To ensure prudent risk management, we imposed constraints on portfolio characteristics. Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of VIX futures indices, ensuring they did not exceed an absolute value of 1. Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30%.
This methodology, integrating forecast-driven optimization within a risk-constrained mean-variance framework, provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation. The application of historical covariance data and the delineation of precise risk parameters contribute to the robustness and reliability of the derived portfolio weights, thereby enhancing the integrity of the investment strategy.

Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place tables after the first paragraph in which they are cited.

@@

\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}

@@

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{data preparation}

\subsection*{experiment design}

\subsubsection*{trading strategies construction (PO)}
Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

@@

\subsection*{Analysis Results}
\subsubsection*{Dataset Contains Term Structure Infomation Stand Out}
In our experiment, we explore three distinct datasets named Simple, TermStructure, Derivations as before, our results show that TermStructure and Derivations with term structure infomation stand out.
\\Table~\ref{Best Dataset} select the best dataset for all models on our main metrics: IC, rank IC, information ratio of long short strategy, information ratio of constrined mean-variance optimization strategy.

\begin{flushleft} The best dataset in all models on main metircs: IC, Rank IC, C-MVO Information Ratio, Long Short Information Ratio.
\end{flushleft}
\label{table1}
% \end{sidewaystable}
\end{adjustwidth}

>>>>

% line numbers
\usepackage[right]{lineno}
\usepackage{geometry}

@@

% array package and thick rules for tables
\usepackage{array}
\usepackage{booktabs}

% self imported package
\usepackage{rotating}
\usepackage{makecell}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Machine Learning Trading Strategy in VIX Derivatives:\\{\textit{A Walk-Forward Training and Backtesting Study}}} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Sangyuan Wang\textsuperscript{1\Yinyang},
Keran Li\textsuperscript{1\Yinyang}
JiaQi Chen \textsuperscript{2,3\textcurrency},
 Liang Xu \textsuperscript{2},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Southwestern University of Finance and Economics, Chengdu, Sichuan, China
\\
%\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
%\\
%\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
%\\
%\bigskip

@@

% Current address notes
\textcurrency Current Address: Southwestern University of Finance and Economics, Chengdu, Sichuan, China % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address
% \textcurrency c Insert third current address

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
We found that information on the VIX futures curve can guide the trading of VIX derivatives. We use two sets of features derived from the VIX futures curve to predict the next day's return rates of VIX ETFs and construct a trading strategy. In this strategy, up to 4 out of 8 different machine learning models achieved an Information Coefficient (IC) value of over 0.02 over a span of 11 years, compared to the MSE and AR(1) baseline models. This indicates that the VIX futures curve indeed has predictive power over VIX ETFs. In a strict Walk-Forward back test, a simple long-short strategy achieved an average information ratio of 1.3. We used Portfolio Overlay (PO) methods to increase the average information ratio to 1.6, demonstrating that the prediction of returns is valuable not only in relative terms but also in absolute terms.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
%\section*{Author summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

%\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
The implied volatility index (VIX), often termed as the “investor fear gauge” , has been a pivtoal index in the financial market after its first inception in early 1990s. Since 2003, VIX reflects the 30 days standard \& poor (S \& P 500) expected volatility implied in various call and put S P 500 options (Whaley, 2009; Cboe, 2023). Due to VIX itself is not directly tradable. Instruments such as VIX futures, options, and Exchange-traded notes(ETN) are utilised as essential tools for trading VIX. Meanwhile, With investors growing interests in VIX, S \& P introduced the VIX futures index series in 2005. This series replicates constant-maturity VIX futures indexes by systematically rolling future contracts with varying maturities. Specifically, the VIX short-term futures Index (SPVXSP) keeps a fixed 1-month constant maturity, the VIX two-month futures index (SPVIX2ME) maintains a constant 2-months maturity, three-month (SPVIX3ME), four-month (SPVIX4ME), five-month (SPVIXMP), and six-month (SPVIX6ME) futures indices, each maintain constant maturities corresponding to their respective timeframes. Fig.\ref{fig1} illustrates the correlations among these six constant maturity futures (CMFs).

\begin{figure}[!h]
\caption{\bf CMfs Correlations}
%\includegraphics[width=0.5\linewidth]{EDA_correlations.png}
\label{fig1}
\end{figure}

The VIX term structures describes the relationship of VIX futures contracts with varying expiration dates.The term structure is in contango when VIX futures with longer maturities have higher prices than futures with shorter maturities, backwardation occurs when prices of VIX futures with shorter time to expiration exceed those with longer maturities. Our empirical analysis,  as showcased in exhibit 1 through K-means clustering, robustly indicates a dominant contango shape within the VIX future term structure. Such phenomenon can be partially explained based on volatility risk premium theory (Carr \& Wu, 2008) and  Johnson (2017) work, which divides VIX term strucuture  into two fundamental components: conditional volatility expectations and risk premiums. It becomes apparent that investors stipulate a larger risk premium for further VIX options, as contrasted with the shorter-maturity VIX options except during certain financial crisis. Notably, the VIX futures term structure holds predictive power when anomalies in the term structure revert to the classical shape given strong mean-reverting property of VIX futures illustrated by Avellaneda and Papanicolaou (2019).
The literature has extensively explored predictive power of implied volatility (IV),  IV term structure and VIX term structure using classical statistical models. Wang and Wang (2016) among others find that incorporating IV can enhance forecast accuracy within the GARCH model framework. Additionally, studies by Bush et al. (2011), Byun and Kim (2013), and Haugom et al. (2014) have demonstrated the informative power of IV using the heterogeneous autoregressive (HAR) model.transitioning towards term structures, few studies confirms the prediction power of term structures for various financial instruments. Chang (2016) shows the information gained in VIX term structure significantly aid in predicting S\&P 500 index returns volatility while Clements (2020) uses HAR model to further affirm that the information derived from IV term structure possesses exceptional predictive power for forecasting both the level and directional changes in stock return volatility, even during the volatile period of the Global Financial Crisis.Chen (2022) employes CHH model and confirms that the volatility factor constructed from swaptions IV term structures holds significant predictive power on excess bond returns. Lastly, Ornelas and Mauad (2019) provides empirical evidence of the IV term structures informative power in forecasting exchange rate returns. Based on the robust findings from above research use classical statistical models to exploit the predictive power of term structures, in this paper, we use HAR model as the baseline to compare with other selected machine approaches.

Despite the booming of machine learning (ML) approaches, relatively scarce studies use machine learning approach to exploit VIX-related issues. Hosker et al (2018) finds that recurrent neural network(RNN) and long short-term memory(LSTM) shows the best performance for forecasting 1-month VIX futures 3-days and 5-days ahead among principal components analysis and ARIMA model. Hirsa and et al. (2021) apply neural network models (random forest, support vector machines, feed-forward neural network and LSTM) to investigate the approaches that could replicate VIX index and VIX futures with fewer options compared to CBOE original methodology. Vrontos (2021) applies various machine learning models and discovers that ML models are statistical and economic superior compared to standard econometric models when forecasting the directional changes of VIX index. Lastly, Avellaneda (2021) generates VIX futures trading signals by including functional dependence of VIX term structures, VIX futures position as well as expected utility in neural network and finds that this approach shows better portfolio performance in the out of sample backtesting.

In this paper, we use multiple types of machine learning models which includes Recurrent neural network models, tree-based model, transformer and graph attention neural network to exploit informative power of VIX futures term structure on next-day return of  VIX constant maturity instruments.

By working closely with Avellaneda (2021) work,we first use information extracted from the VIX term structure to construct various VIX term-structure-related features and combine major financial market features, we then implement various machine learning methods to predict the next day return of six VIX constant-maturity instruments. Lastly, to evaluate the economic performances of our work, we utilise machine learning prediction results as trading signals to implement two trading strategies: The long-short strategy and mean-variance-adjusted portfolio optimization strategy. Our results reveal that the VIX term structure has superior informative power in predicting the return of VIX constant-maturity instruments.

The key contributions of this study can be summarised as follows, first, based on the VIX futures term structures decomposition approach proposed by Avellaneda(2021), features with term-structure information, personal information, and major market trends information are included in the datasets. Second, various state-of-art machine learning approaches are introduced to predict the VIX rolling-ETFs next-day returns. Third, two trading strategies are used in the backtesting which are, the long-short strategy based on machine learning ranking and a mean-variance adjusted portfolio optimization strategy.
The results reveal that firstly, the VIX futures curve has the ability to predict the next-day return of VIX ETFs. Thirdly, The economic performance of machine learning models relying on the adjusted mean-variance portfolio optimization strategy generally outperforms that of models based on the long-short strategy. The remainder of the paper is composed as follows: Section 2 provides proposed research methodology(1.VIX term structures decompositions 2.machine learning models) section 3 describes data and experiment design, Section 4 analysis results, Section 5 concludes and discuss, Appendix: graph and code.

\section*{Research Methodologies and Data}
\subsection*{1. Trading signals constructions}
The VIX is calculated by the Chicago Board Options Exchange (CBOE) and is based on the prices of options on the S\&P 500 Index.
\\Let $t$ denote time and let $VIX_t$ denote the value of VIX on that date. At time $t$,
we can view lots of VIX futures contracts with different expiration dates:
\begin{eqnarray}
    {F^i_t} := \text{VIX futures expiring at time $T_i$ at time t}
\end{eqnarray}
where $i$ denote the index of the VIX futures contracts with a ascending expiration dates $T_1 < T_2 < ... < T_d$.
\\A term-structure of constant-maturity VIX futures(CMFs), consist of 1,2,...,6 months in our case, are constructed as
a linear interpolation of two nearest expiration dates VIX futures:
\begin{eqnarray}
\label{eq:defineV}
    {V^j_t} := \omega^j_tF^{L_j}_t\ + (1 - \omega^j_t)F^{R_j}_t \text{for j in \{1,2,...,6\}}
\end{eqnarray}
where $L_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the left of time axis,
$R_j$ represents the VIX futures of the nearest expiration dates close to $j$-month on the right of time axis, and
$\omega^j_t = \frac{T_{R_j} - 30j}{T_{R_j} - T_{L_j}}$. Note that $VIX_t$ is like a zero-horizon CMF.
CMFs are commonly used for they do not suffer fluctuations caused by contract expiry.

@@

\subsection*{2. Proposed Machine Learning Algorithms}

@@

(introduction of MLP).
In our experiment, we use leaky ReLU introduced by Mass (2013) as the activation function \(\phi\) for MLP, the mathematical expression of leaky ReLU  is shown in Eq.2. Given activation function \(\phi\), features \(X \in R^ {n\times d}\) where \(x\) presents the batch size and \(d\) presents the dimensionalities
\begin{eqnarray}
\label{eq:schemeP}
\mathrm{\phi^{(i)}} =\mathbf{max({W^{(i)}}^{T}x,0)}=
\begin{cases}
\mathbf{{W^{(i)}}^{T}x},\quad &\mathbf{{W^{(i)}}^{T}x}>0\\0, \quad else
\end{cases}
\end{eqnarray}
where \(W^{(i)}\) is the weight vector of \(i_{th}\) hidden unit while \(x\) is the input features. A naive MLP can be illustrated as fig.\ref{MLP}
\begin{figure}[!h]
%\includegraphics[width=0.5\linewidth]{MLP.jpg}
\caption{{\bf Naive MLP}}
\label{MLP}
\end{figure}

@@

\subsubsection*{2.4 Temporal Covolutional Networks}
Temporal covolutional networks (TCN), originally introduced by Lea et al. (2016), is a type of neural network that employs convolutional layers to capture dependencies in sequential data. Unlike traditional RNN and LSTMs, TCNs use 1D convolutions to process input sequences in parallel, making them highly parallelizable and capable of capturing long-range dependencies. Implementation details can be found in eq.5.

@@

\subsubsection* {2.5 Transformer}
We also implement attention-based network architecture called transformer proposed by Vaswani et al. (2017) for prediction. Transformer departs from the traditional recurrent or convolutional layers, relying instead on the attention mechanism, This enables the model to weigh the significance of different parts of the input data differently, allowing it to capture complex dependencies and relationships within the data. Eq. illustrates the implementation details.

\begin{eqnarray}
\label{eq: Transformer}
    y_i = F(encoder(X), decoder(y_1,...,y_{i - 1}))
\end{eqnarray}
In our case, we only use encoder to produce output, for we don't need to produce output one by one. Encoder's framework follows by:
\begin{eqnarray}
\label{eq: TransformerDecoder}
    \begin {cases} \tilde{X} = \text{Positional Encoding} + X
    \\Y = FFN(\text{self-attention}(X))
    \end {cases}
\end{eqnarray}
where FFN is a feedforward network with residual added and layer norm, self-attention's framework follows by:
\begin{eqnarray}
\label{eq: self-attention}
    \begin {cases} Q = W^QX
    \\K = W^KX
    \\V = W^VX
    \\Z = \test{softmax}(QK^T)V
    \end {cases}
\end{eqnarray}
where $Z$ is the output of self-attention layer.
\subsection*{Data Preparations and Experiment Designs}

@@

 \subsubsection*{Empirical Experiment Designs}
 The main goal of our empirical experiment aims to evaluate the statistical and economic performances among different models and different datasets. Before training, we are dealing with 6 groups of instruments and features under a single date as shown in table 1,2 and 3. Based on the concept of "feature stacking", we combine 6 groups of instruments and features into one large group to achieve a more general conclusions. Meanwhile, the model is less biased by outliers and over-fitting is less likely to occur while correlations among CMFs are considered in the model. During training, cross-validation is widely used to determine the generalization error of an ML algorithm, so as to prevent over fitting. However, CV can be exposed to future information leakage, particularly in time-series data due to various reasons such as the inclusion of future data points caused by random sampling, the temporal dependencies of financial time-series data, etc. Therefore, to avoid the leakage of future information, we implement a walk-forward training and back-testing procedure, specifically, We set (First-Train, First-Valid, First-Test) as follows: First Train: (2005-12-20, 2010-06-30), First Valid: (2010-07-01, 2010-12-31), First Test: [2011-01-01, 2022-08-15]. This setup is based on three main considerations: 1. To ensure a sufficiently long back testing period of 11 years; 2. To ensure the first training set is large enough and includes extreme market conditions like the 2008 financial crisis; 3. To set a six-month valid set, ensuring the training data used for predictions is at least six months old, which further prevents information leakage and increases robustness. We believe that using more recent data in practice can yield better results. Additionally, we follow an expanding window process  when using the data, meaning each training includes all previous data points, to train a more robust model for prediction.

 \begin{algorithm}
        \caption{walking forward procedure}
        \begin{algorithmic}
            \STATE $rollingtasks \gets Algorithm TaskRollGen\ref{Task_Roll_Gen}$
            \FOR{$task \gets rollingtasks$}
            \STATE $model \xleftarrow{fit} task[train]$
            \STATE $pred \xleftarrow{predict} task[test]$
            \STATE $preds \xleftarrow{append} pred$
            \ENDFOR
            \STATE $PRED \xleftarrow{concat} preds \text{\quad \# PRED is a time series cover Task[test]'s horizon}$
            \STATE $metrics \xleftarrow{calculate} PRED$
            \STATE $backtestingresult \gets PRED, strategy \text{\quad \# bar by bar}$
        \end{algorithmic}
\end{algorithm}
\begin{algorithm}
	\renewcommand{\algorithmicrequire}{\textbf{Input:}}
	\renewcommand{\algorithmicensure}{\textbf{Output:}}
	\caption{Task Roll Gen}
	\label{Task_Roll_Gen}
	\begin{algorithmic}
    	\REQUIRE TASK contains \{TRAIN, VALID, TEST, roll\_lenth\}
            \ENSURE rollingtasks with their own \{train, valid, test\}
            \STATE $fragments \gets$ Test divided by roll\_lenth
            \FOR{$m \gets fragments$}
            \STATE $task \gets Task$
            \STATE $task[test] \gets m$
            \STATE $task[valid] \gets [start\_date_{test} - 1 - lenth_{Valid}, start\_date_{test} - 1]$
            \STATE $task[train] \gets [start\_date_{TRAIN}, strat\_date_{valid} - 1]$ \text{\quad \# expanding}
            \STATE $rollingtasks \xleftarrow{append} task$
            \ENDFOR
	\end{algorithmic}
\end{algorithm}

\subsubsection*{Back-testing Performance Evaluation Methods:  Constrained-mean-variance Optimization (C-MVO) strategy \& Long-short strategy}

We introduce both C-MVO strategy and long-short strategy to explore the backtesting performances among various machine learning models. The following is the detailed explanation for two strategies.  In line with the classical mean-variance portfolio optimization structure proposed by Markowits (1952).  For C-MVO strategy, we incorporated several additional constraints. The \(Cov_{port}\) was derived through the estimation of a 60-days historical covariance matrix. The risk aversion parameter, denoted as \(gamma\), was fixed at a value of 0.2. To ensure prudent risk management, we imposed constraints based on portfolio characteristics. Specifically, we restricted gross leverage to a maximum of 3, and imposed absolute limits on the individual weights of cmfs, ensuring individual weights did not exceed an absolute value of 1. Furthermore, a critical risk threshold was established, with the annualized risk of the portfolio constrained to not exceed 30 \%.
This strategy provides a rigorous approach to portfolio construction, striking a balance between expected returns and risk mitigation. The application of historical covariance data and the delineation of precise risk parameters contribute to the robustness and reliability of the derived portfolio weights, thereby enhancing the integrity of the investment strategy. The detailed optimization function is represented in eq.\ref{MVO}
 For long-short strategy, which is a common trading strategy aims to exploit profits from relative performances of assets through a combination of long and short positions. In our strategy design,we rank six \(Cmfs\) instrument based on predicted returns in descending order.  Each trading day, we maintain a 50\% long positions in the Cmfs with largest predicted return and a 50\% short position to the lowest predicted return Cmfs, with daily re-balance.
\begin{eqnarray}
\label{MVO}
    Max_{w_i}: \quad & \sum_{i=1}^{n} (W_i \times R_i)-gamma \times risk \nonumber \\
\text{s.t.:} \quad & max(|w_i|) \leq 1 \nonumber \\
                         & \sum_{i=1}^{N} |w_i| \leq 3 \\
        & \left| \sum_{i=1}^{N} w_i \right| \leq 2 \nonumber \\
        & risk \leq risk_{max} \nonumber \\
        & where \quad risk=W_i \times Cov_{port} \times W_{i}^T, \nonumber \\
        & risk_{max}=0.03, \quad gamma=0.2 \nonumber
\end{eqnarray}

% For figure citations, please use "Fig" instead of "Figure".

% Results and Discussion can be combined.
\section*{Results}
Panel.\ref{summary} presents the combined results of predictive and back-testing performances, To assess prediction performance across all machine learning models, we have employed a range of metrics within the domain of quantitative trading evaluation systems. Our major metric is the information coefficient (IC), a statistical measure that quantifies the correlations between predictions of returns and subsequent realized returns of portfolio which can be denoted as \(Corr(\hat{y},{y})\)  A high positive IC indicates a robust predictions are highly correlated with actual returns, suggesting a strong predictive ability. Conversely, a low or negative IC suggests inaccuracies in prediction or even contrarian to actual outcomes. Furthermore, we have integrated ICIR (Information Coefficient Information Ratio) into our evaluation, which can be calculated as Eq.\ref{ICIR}. In addition, we have introduced Rank IC that replace \(Corr(\hat{y},{y})\) as the correlation of returns rankings denoted as \(Corr(\hat{rank},{rank})\) and subsequently computed Rank ICIR. We consider information ratios and annualised returns as key indicators for the assessments of back-testing performances.

\begin{eqnarray}
\label{ICIR}
IR \approx \frac{\bar{IC}}{Std(IC)}
\end{eqnarray}

@@

\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{summary}
% \end{sidewaystable}
\end{adjustwidth}
\end{table}

\subsection*{Term Structure and statistical Derivations evaluation}
Initially, from the perspective of three datasets, based on panel.\ref{summary}, for the predictive performances, models with simple datasets have shown the worst IC compared to the rest of two datasets containing term structure factors and time-series derivations. Notably, GRU (\textit{-0.023}), LGB(\textit{-0.024}), LSTM(\textit{-0.015}) and MLP(\textit{-0.002}) even shows negative IC which indicates the predicted returns are contrast with realised returns.
by following this perspective, we discover  first findings that the robust informative power of term structure factors exists which will be explained in details in the following subsections. In our experiment, we explore three distinct datasets named Simple, TermStructure, Derivations as before, our results show that TermStructure and Derivations with term structure infomation stand out.
\\Table~\ref{Best Dataset} select the best dataset for all models on our main metrics: IC, rank IC, information ratio of long short strategy, information ratio of constrined mean-variance optimization strategy.

\begin{flushleft} The best dataset in all models on main metircs: IC, Rank IC, C-MVO Information Ratio, Long Short Information Ratio.
\end{flushleft}
\label{table1}
\end{adjustwidth}

\subsection*{Informative Power of Term Structures}
\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Statistic Metric}
% \begin{sidewaystable}
\begin{tabular}{lrrrr}
\toprule
{} &     IC &   ICIR &  Rank IC &  Rank ICIR \\
model  &        &        &          &            \\
\midrule
ALSTM  &  0.029 &  0.042 &    0.026 &      0.041 \\
GRU    &  0.004 &  0.006 &    0.002 &      0.004 \\
LGB    &  0.035 &  0.066 &    0.054 &      0.079 \\
LSTM   &  0.021 &  0.031 &    0.016 &      0.026 \\
Linear &  0.114 &  0.162 &    0.091 &      0.152 \\
MLP    &  0.011 &  0.017 &    0.012 &      0.020 \\
XGB    &  0.047 &  0.071 &    0.043 &      0.069 \\
mean   &  0.037 &  0.056 &    0.035 &      0.056 \\
\bottomrule
\end{tabular}

\begin{flushleft}
Table notes: performance of statistic metric
\end{flushleft}
\label{table1}
% \end{sidewaystable}
%\end{adjustwidth}

@@

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Statistic Metric}
% \begin{sidewaystable}
\begin{tabular}{lp{1.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
\toprule
{} &  C-MVO Annualized Return &  C-MVO Information Ratio &  Long Short Annualized Return &  Long Short Information Ratio \\
model  &                          &                          &                               &                               \\
\midrule
ALSTM  &                    0.071 &                    0.744 &                         0.112 &                         0.579 \\
GRU    &                    0.028 &                    0.241 &                         0.080 &                         0.409 \\
LGB    &                    0.023 &                    0.327 &                        -0.085 &                        -0.367 \\
LSTM   &                    0.059 &                    0.671 &                         0.034 &                         0.168 \\
Linear &                    0.150 &                    2.291 &                         0.214 &                         1.105 \\
MLP    &                    0.013 &                    0.043 &                         0.050 &                         0.302 \\
XGB    &                    0.011 &                    0.044 &                         0.116 &                         0.632 \\
mean   &                    0.051 &                    0.623 &                         0.074 &                         0.404 \\
\bottomrule
\end{tabular}

\begin{flushleft}
Table notes: performance of backtest metric
\end{flushleft}
\label{table1}
% \end{sidewaystable}
%\end{adjustwidth}

\subsection*{Strategies Comparison}

@@
